MLExplain

### 2017-10-23 jfla/paper.tex
meilleur figure

\usepackage{tikz}
\usetikzlibrary{positioning}
\usetikzlibrary{fit}

@@

\begin{figure}[ht]
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpréteur en fOCaml};
    \node (fjs) [draw, above right = 0.5cm and 1cm of focaml, text width=2cm] 
{Interpréteur en fJS};
    \node (fjsa) [draw, below right = 0.5cm and 1cm of focaml, text width=2cm] 
{Interpréteur annoté en fJS};
    \node (ast) [draw, right = of fjsa, text width=2cm] {AST};
    \node (source) [draw, right = of fjs, text width=2cm, text centered] 
{Programme};
    \node [draw, dotted, fit=(fjs) (fjsa) (ast)] {page web};
    \draw[->] (focaml.north east) -- node[left] {compilateur} (fjs.south west) ;
    \draw[->] (focaml.south east) -- node[left] {compilateur} (fjsa.north west);
    \draw[->] (source) -- node [right] {Esprima} (ast);
  \end{tikzpicture}

>>>>

\usepackage{tikz}
\usetikzlibrary{positioning,fit,shapes,arrows.meta}

@@

\begin{figure}[ht]
  \begin{center}
  \begin{tikzpicture}[nodes = {align = center}]
    \node (focaml) [draw, text width=2cm] {Interpréteur et librairies en fOCaml};
    \node (fjs) [draw, right = 1cm of focaml, text width=2cm, rectangle split, rectangle split parts=2, text centered] 
{Librairies en fJS \nodepart{second} Interpréteur annoté en fJS};
    \node (ast) [draw, above = of fjs, text width=2cm] {AST du programme interprété};
    \node (source) [draw, right = 2cm of ast, text width=2cm, text centered] 
{Programme interprété};
    \node [draw, dotted, fit=(fjs) (ast) (source)] {page web};
    \node (trace) [draw, right = 2cm of fjs, text width=2cm, text centered] 
{Trace};
    \path[->,thick,>=stealth] (focaml.north east) edge[bend left] node[above left] {compilateur} (fjs.north west) ;
    \path[->,thick,>=stealth] (focaml.south east) edge[bend right] node[below left] {\parbox{2cm}{\centering compilateur annotant}} (fjs.south west);
    \path[->,thick,dotted,>=stealth] (source) edge node [above] {Esprima} (ast);
    \path[->,thick,dotted,>=stealth] (ast) edge (fjs);
    \path[->,thick,dotted,>=stealth] (ast) edge (fjs);
    \path[->,thick,dotted,>=stealth] (fjs) edge (trace);
  \end{tikzpicture}
  \end{center}
